%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer \& Backend developer} % Job title
    {Tagaddod (Green-Pan)} % Organization
    {Cairo, Egypt} % Location
    {Jul. 2024 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Working on the main project
          % Currently working on base app infrastructure to be able to expand our product in multiple countries.
        }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Country’s Military, Service Member} % Job title
    {Mandatory Military Service} % Organization
    {Cairo, Egypt} % Location
    {Apr. 2023 - Jun. 2024 } % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Demonstrated discipline, leadership, and a strong sense of duty during successful completion of mandatory military service.}
        \item {Acquired skills in teamwork, time management, and problem-solving while working under pressure.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer \& Backend developer} % Job title
    {Tagaddod (Green-Pan)} % Organization
    {Cairo, Egypt} % Location
    {Oct. 2022 - Apr. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Refactored 85\% of warehouse management flow, maintaining 70\% testing coverage which reduced error rates in production.}
        \item {Introduced automated tests and began implementing TDD for multiple flows to improve testing procedures}
        \item {Implemented Docker to containerize the main project, enhancing communication and development efficiency within the team.}
        \item {Led core database recovery after a critical incident by utilizing MySQL bin-log files to restore its latest valid state.
                    % Also helped restoring missing data in multiple tables in the core database as a result for an intrusion incident.
              }
        \item {Facilitated onboarding process for new engineers to align tasks, set expectations, and enhance productivity.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Backend developer} % Job title
    {Akwad} % Organization
    {Cairo, Egypt} % Location
    {Aug. 2022 - Sep. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Received the main projects handover, so that any new team can be onboarded easily and eliminating any knowledge bottlenecks in the team.}
        \item {Reduce our 2 main forms time complexity from nearly 1.5 minutes to 200 milliseconds, which is 450\% better than before.}
        \item {Optimized multiple SQL queries using the known database design techniques to normalize the database scheme according to our needs.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Mobile developer (Outsourced)} % Job title
    {AUB (Ahli United Bank)} % Organization
    {Cairo, Egypt} % Location
    {Aug. 2021 - Oct. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed the main custody application within a limited margin.}
        \item {I was responsible for communicating with an external penetration-testing team. And implemented RASP security layer for the application.}
        \item {Involved in the integration process with the core-banking system and the central SMS authentication-service.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Mobile developer} % Job title
    {Akwad} % Organization
    {Cairo, Egypt} % Location
    {Jan. 2020 - Aug. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        % TODO:: I think here I should add href for each package
        \item {Developed multiple in house packages that our projects depend on. For example:}
        \begin{itemize}
          \item {Auth-Provider~\rightarrow~An authentication package to handle email/phone/social login methods.}
          \item {Form-Builder~\rightarrow~Provides a generic way to generate forms statically and dynamically.}
          \item {Notifier~\rightarrow~A dynamic package to handle sending push notifications for users with different types of payloads with dynamic action decided by the backend.}
        \end{itemize}
        \item {I was responsible for designing a new flexible main-structure for our projects.}
        \item {Provided support for most of the GIT problems that the team faced.}
        \item {Supported for bug fixing nearly 65\% of our main project "GreenPan" across 6 months.}
        \item {Migrated nearly all our main projects to null-safe flutter version, which resulted in less error rates.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Trainee} % Job title
    {Akwad} % Organization
    {Cairo, Egypt} % Location
    {Nov. 2019 - Dec. 2019} % Date(s)
    {
      \begin{cvitems}
        \item {Fixed multiple high priority bugs on the production apps.}
        \item {Investigated and fixed media/camera bugs that happened on specific devices on production.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Mobile developer} % Job title
    {Freelancer} % Organization
    {Cairo, Egypt} % Location
    {Aug. 2019 - Oct. 2019} % Date(s)
    {
      \begin{cvitems}
        Worked with multiple clients to deliver small mobile apps, and all of them integrate with Firebase as the backend.
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
  