%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer \& Backend developer} % Job title
    {Tagaddod (Green-Pan)} % Organization
    {Cairo, Egypt} % Location
    {Jul. 2024 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {More achievements are comming !
          % Currently working on base app infrastructure to be able to expand our product in multiple countries.
        }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Country’s Military, Service Member} % Job title
    {Mandatory Military Service} % Organization
    {Cairo, Egypt} % Location
    {Apr. 2023 - Jun. 2024 } % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Demonstrated discipline, leadership, and a strong sense of duty during successful completion of mandatory military service.}
        \item {Acquired skills in teamwork, time management, and problem-solving while working under pressure.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer \& Backend developer} % Job title
    {Tagaddod (Green-Pan)} % Organization
    {Cairo, Egypt} % Location
    {Oct. 2022 - Apr. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Refactored 85\% of warehouse management flow, maintaining 70\% testing coverage which reduced error rates in production.}
        \item {Introduced automated tests and began implementing TDD for multiple flows to improve testing procedures}
        \item {Implemented Docker to containerize the main project, enhancing communication and development efficiency within the team.}
        \item {Led core database recovery after a critical incident by utilizing MySQL bin-log files to restore its latest valid state.
                    % Also helped restoring missing data in multiple tables in the core database as a result for an intrusion incident.
              }
        \item {Facilitated onboarding process for new engineers to align tasks, set expectations, and enhance productivity.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Backend developer} % Job title
    {Akwad} % Organization
    {Cairo, Egypt} % Location
    {Aug. 2022 - Sep. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Onboarding new team members and eliminating knowledge bottlenecks in the team.}
        \item {Reduce 2 of the main forms' time complexity from nearly 1.5 minutes to 200 milliseconds, which is 450\% better than before.}
        \item {Optimized multiple SQL queries using database design techniques, and normalizing database schemes according to needs.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Mobile developer (Outsourced)} % Job title
    {AUB (Ahli United Bank)} % Organization
    {Cairo, Egypt} % Location
    {Aug. 2021 - Oct. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developing the main custody application within a tight time margin.}
        \item {Led the communication with the external penetration-testing team, and implementating RASP security layer.}
        \item {Involved in the integration process with the core banking system and the central SMS authentication service.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Mobile developer} % Job title
    {Akwad} % Organization
    {Cairo, Egypt} % Location
    {Nov. 2020 - Aug. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        % TODO:: I think here I should add href for each package
        \item {Working on multiple in-house packages that serve end products.}
        \item {Supporting bug fixing, nearly 65\% of our ongoing project across 6 months.}
        \item {Migrated nearly all ongoing projects to null-safe flutter version, which resulted in lower error rates.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
